\blue{...Numerical investigation of viscous flow instabilities through heterogeneous porous media using adaptive and unstructured meshes under different mobility scenarios...}

### 2017-07-11 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

In Section~\ref{section:results_homo_hete}, the impact of viscosity ratio on the growth of fingers and the triggering effect of heterogeneity on instability's nucleation were demonstrated in modified simulated Hele-Shaw cells. In order to capture the continuous development of such viscous instabilities, mesh grids  with sufficient resolution need to be applied over the interface between fluids.

>>>>

In Section~\ref{section:results_homo_hete}, the impact of viscosity ratio on the growth of fingers and the triggering effect of heterogeneity on instability's nucleation were demonstrated in modified simulated Hele-Shaw cells. In order to capture the continuous development of viscous instabilities, mesh grids with sufficient resolution need to be applied over the interface between fluids. In this section, numerical simulations were conducted with distinct mesh resolutions to qualitatively assess model capability to capture fingers growth. In order to trigger the formation of fingers, regions with sharp permeability gradient were introduced (Fig.~\ref{fig:testcase_heter_domain}a).
